Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-06-25 paper/paper.Rmd
update llto figure
upd spatiotemp intro

Some methods have the ability to operate in multiple spaces, i.e. spatial, temporal or spatiotemporal (2D + time).
To avoid redundancy and putting too much weight on certain methods, only the spatiotemporal examples of these methods will be shown in the following sections.
However, these can be adapted for the respective other cases (spatial only, temporal only).

@@

```{r llto, echo=FALSE, out.width="90%", fig.cap="Three-dimensional visualization of method 'sptcv\\_cstf' and sub-method 'Leave-Location-And-Time-Out' (LLTO). The grey points show the points omitted by this method.", fig.pos="ht"}
knitr::include_graphics("llto.png")
```

>>>>

Some methods have the ability to operate in multiple spaces, i.e. spatial, temporal or spatiotemporal (2D + time).
To avoid redundancy and putting too much weight on certain methods, only the spatiotemporal examples of these methods will be shown in the following sections.
For the respective other spaces, usually only one of the space or time variable inputs needs to be omitted.

@@

```{r llto, echo=FALSE, out.width="90%", fig.cap="Three-dimensional visualization of method 'sptcv\\_cstf' and sub-method 'Leave-Location-And-Time-Out' (LLTO). The grey points show the points omitted by this method, i.e. the points which are not used in the training or test set in this fold.", fig.pos="ht"}
knitr::include_graphics("llto.png")
```
